Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-09 paper/structureScene.tex
checking VL questions

The same dichotomy applies for the field of audio scene analysis, where the interest can be whether 1) to isolate and identify precise events, \textit{i.e.} acoustic event detection (AED) or 2) to predict global attributes assigned to large time spans of audio, \textit{i.e.} ASC. For the latter, most state-of-the-art systems roughly follow the bag of frame approach (BOF) initiated in \cite{aucouturier2007bag} where the audio is modelled as high level statistics computed from a set of local features. Even though this approach as the advantage of high genericity and follows some evidence found by psycho perception research \cite{macdermott}, for the specific implementation with gaussian mixture models (GMMs) of Mel-frequency cepstral coefficients (MFCCs) it is demonstrated to be perform equivalently compared to a mere point averaging of the features  \cite{lagrange:hal-01082501}.

@@

\begin{figure}
\begin{center}
\setlength{\unitlength}{1cm}
\begin{picture}(5,2)
 \put(-1.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q8.png}}
 \put(2.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q1.png}}
\end{picture}
\caption{
\label{fig:gammatones}
Left: Gammatone wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$ with a quality factor of $Q_1=8$.
Right: Gammatone wavelet $\boldsymbol{\psi_{\gamma_2}}(t)$ with a quality factor of $Q_2=1$.
\vl{we should discuss color schemes and axis labels}}
\end{center}
\end{figure}

@@

This strategy is already widespread in the literature.
For instance, we should note that \cite{roma2013}, who secured the first place in the 2013 edition of the DCASE challenge, rely on cepstral descriptors computed up to a cutoff frequency as small as $\xi_{1,\max}  = 900\,\mathrm{Hz}$ instead of the more conventional value of $16\,\mathrm{kHz}$.
\vl{Qu'en penses-tu ML ?}

\subsection{Logarithmic compression}
Many algorithms in pattern recognition, including nearest neighbor classifiers and support vector machines, tend to work best when all features follow a standard normal distribution across all training instances.
Yet, because of the complex modulus nonlinearity, scattering coefficients are nonnegative by design.
It appears empirically that their distribution is skewed towards the right, which means that the tail towards greater values is longer than the tail towards lower values.
However, skewness can be reduced by applying to all coefficients a pointwise concave transformation, \eg logarithmic.
Figure \ref{fig:histograms} shows the distribution of an arbitrarily chosen scattering coefficient over the DCASE 2013 dataset, before and after logarithmic compression.
\vl{Qu'en penses-tu ML ?}

>>>>

The same dichotomy applies for the field of audio scene analysis, where the interest can be whether 1) to isolate and identify precise events, \textit{i.e.} acoustic event detection (AED) or 2) to predict global attributes assigned to large time spans of audio, \textit{i.e.} ASC. For the latter, most state-of-the-art systems roughly follow the bag of frame approach (BOF) initiated in \cite{aucouturier2007bag} where the audio is modelled as high level statistics computed from a set of local features. Even though this approach as the advantage of high genericity and follows some evidence found by psycho perception research \cite{mcdermott2013summary}, for the specific implementation with gaussian mixture models (GMMs) of Mel-frequency cepstral coefficients (MFCCs) it is demonstrated to be perform equivalently compared to a mere point averaging of the features  \cite{lagrange:hal-01082501}.

@@

\begin{figure}
\begin{center}
\setlength{\unitlength}{1cm}
\begin{picture}(5,2)
 \put(-1.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q8.png}}
 \put(2.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q1.png}}
\end{picture}
\caption{
\label{fig:gammatones}
Left: Gammatone wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$ with a quality factor of $Q_1=8$.
Right: Gammatone wavelet $\boldsymbol{\psi_{\gamma_2}}(t)$ with a quality factor of $Q_2=1$.
\vl{we should discuss color schemes and axis labels} \ml{yes we should but for the second submission, go ahead}}
\end{center}
\end{figure}

@@

Reducing the frequency range is an effective way to enhance invariance, widely used in the literature.
For instance, \cite{roma2013} achieved the best performance in the 2013 edition of the DCASE challenge, rely on cepstral descriptors computed up to a cutoff frequency as small as $\xi_{1,\max}  = 900\,\mathrm{Hz}$ instead of the more conventional value of $16\,\mathrm{kHz}$.
\vl{Qu'en penses-tu ML ?}
\ml{j'ai un peu reformuler}

\subsection{Logarithmic compression}
Many algorithms in pattern recognition, including nearest neighbor classifiers and support vector machines, tend to work best when all features follow a standard normal distribution across all training instances.
Yet, because of the complex modulus nonlinearity, scattering coefficients are nonnegative by design.
It appears empirically that their distribution is skewed towards the right, which means that the tail towards greater values is longer than the tail towards lower values.
However, skewness can be reduced by applying to all coefficients a pointwise concave transformation, \eg logarithmic.
Figure \ref{fig:histograms} shows the distribution of an arbitrarily chosen scattering coefficient over the DCASE 2013 dataset, before and after logarithmic compression.
\vl{Qu'en penses-tu ML ?}
\ml{tres bien, mettre les deux distributions de couleurs differentes}
